Races with hyper3 objects

### 2022-08-08 inst/race3.Rmd
point to the javelin analysis
more work on constructors comparing mercedes from 2020-2021

@@

```{r,label=saveconstructordataset}
save(
constructor_2021_maxp,
constructor_2021,
constructor_2021_table,
file="constructor.rda")
```

>>>>

# Constructors' championship 2020

```{r,label=constructor2020,cache=TRUE}
jj <- read.table("constructor_2020.txt",header=TRUE)
i <- seq(from=1,by=2,to=nrow(jj)) # extract every second entry for points
constructor_points_2020 <- jj[i,ncol(jj)]
names(constructor_points_2020) <- jj[i,1]

constructor_points_2020 <- sort(constructor_points_2020,dec=TRUE)
constructor_points_2020

constructor_table_2020 <- jj[,-ncol(jj)]
constructor_table_2020[,1:17]
constructor_2020_table <- constructor_table_2020
constructor_2020 <- ordertable2supp3(constructor_table_2020)
```

```{r,label=maxpconstructor2020,cache=TRUE}
constructor_2020_maxp <- maxp(constructor_2020,n=1)
constructor_2020_maxp <- sort(constructor_2020_maxp,dec=TRUE)
constructor_2021_maxp <- sort(constructor_2021_maxp,dec=TRUE)
constructor_2020_maxp
constructor_2021_maxp
```

```{r,label=changenames,cache=TRUE}
constructor_2020_and_2021 <- psubs(constructor_2020,"Merc","Merc2020") + psubs(constructor_2021,"Merc","Merc2021")
```

```{r,doconstructor20202021test,cache=TRUE}
ans <- samep.test(constructor_2020_and_2021,c("Merc2020","Merc2021"))
```

```{r,show20201test}
ans
```

Note that the analysis in `javelin.Rmd` is appropriate here too, a
nice example.

@@

```{r,label=saveconstructordataset}
save(
constructor_2020_maxp,constructor_2020,constructor_2020_table,
constructor_2021_maxp,constructor_2021,constructor_2021_table,
file="constructor.rda")
```
